Hurricane Evacuation Strategies for the State of Mississippi

### 2015-11-16 manuscript.tex
Added start of contributions section

\section{Individual Contributions}
\label{sec:contributions}
  \begin{thebibliography}{9}
    \bibitem{county_map}
      \url{http://www.madeinmississippi.us/wp-content/uploads/2015/02/mississippi-county-map.jpg}
    \bibitem{ms_highways}
      \url{https://www.mississippi.org/assets/docs/library/ms_highways.pdf}
    \bibitem{pmc}
      \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4060166/}
    \bibitem{5news}
      \url{http://5newsonline.com/2012/08/27/garretts-blog-hurricanes-in-arkansas/}
    \bibitem{famsize}
      \url{http://www.statista.com/statistics/183657/average-size-of-a-family-in-the-us/}
    \bibitem{graphtool}
      \url{http://graph-tool.skewed.de/}
    \bibitem{census}
      \url{http://census.ire.org/data/bulkdata.html}
  \end{thebibliography}

>>>>

\section{Individual Contributions}
\label{sec:contributions}
\subsection*{Ryan}
Performed the data-fetching of the hurricanes. Wrote all of the most of the manuscript with Paul. Worked out some of the logic for both the flow and the markov model.

\subsection*{Paul}
Designed and implemented the stochastic model. Helped Ryan write most of the manuscript. Parsed the county data such as county location and population using the WolframAlpha API.

\subsection*{Antoine}
Implemented the flow and Markov models. Created almost all of the graph and network visualizations. Worked on the two first models' analyses for the manuscript.

  \begin{thebibliography}{9}
    \bibitem{county_map}
      \url{http://www.madeinmississippi.us/wp-content/uploads/2015/02/mississippi-county-map.jpg}
    \bibitem{ms_highways}
      \url{https://www.mississippi.org/assets/docs/library/ms_highways.pdf}
    \bibitem{pmc}
      \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4060166/}
    \bibitem{5news}
      \url{http://5newsonline.com/2012/08/27/garretts-blog-hurricanes-in-arkansas/}
    \bibitem{famsize}
      \url{http://www.statista.com/statistics/183657/average-size-of-a-family-in-the-us/}
    \bibitem{graphtool}
      \url{http://graph-tool.skewed.de/}
    \bibitem{census}
      \url{http://census.ire.org/data/bulkdata.html}
  \end{thebibliography}
